Clustering based on probability distributions with application on residential customers

### 2021-10-19 main.Rmd
adding all codes in scripts

```{r tab-distribution, fig.pos="htb"}
granularity = c("g1", "g2", "g3")
alternate_design =  c("g10 ~ N(0, 1), g11 ~ N(2, 1)",
                      "g21 ~ N(2, 1), g22 ~ N(1, 1), g23 ~ N(0, 1)",
                      "g31 ~ N(0, 1), g32 ~ N(1, 1), g33 ~ N(2, 1), g34 ~ N(1, 1), g35 ~ N(0, 1)")

# alternate_design =  c("g11 ~ N(2, 1)",
#                       "g21 ~ N(2, 1), g22 ~ N(1, 1)",
#                       "g32 ~ N(1, 1), g33 ~ N(2, 1), g34 ~ N(1, 1)")

tab_dist <- tibble::tibble(granularity = granularity, `Varying distributions` = alternate_design)

# knitr::kable(tab_dist, caption = "Alternate distributions of different categories if they deviate from null.")
```

```{r tab-design}
design = c("design-1", "design-2", "design-3", "design-4", "design-5")
g1 = c("fixed", "vary", "fixed", "fixed", "vary")
g2 = c("fixed", "fixed", "vary", "fixed", "vary")
g3 = c("fixed", "fixed", "fixed", "vary", "vary")
table <- tibble(design, g1, g2, g3)

#%>% kable(caption = "5 different designs resulting from considering different distributions across categories.")
```

```{r tab-dist-design}

# library(kableExtra)
# 
# knitr::kables(list(kable(caption = "Alternate distributions of different categories if they deviate from null.",
#    tab_dist
#     ) %>% kable_styling(),
#   kable(caption = "5 different designs resulting from considering different distributions across categories.",
#  tibble(design, g1, g2, g3)
#     ) %>% kable_styling()
#   )
# ) %>% kable_styling()
# 
knitr::kable(
  list(tab_dist,  tibble(design, g1, g2, g3)),
  caption = 'For Scenario (a), distributions of different categories (top), 5 designs resulting from different distributions across categories (below)',
  booktabs = TRUE, valign = 't'
)
```

```{r generate-design-3change}
generate_design <- function(t, mu1, mu2, mu3){

g1_dvary <- rep(mu1, length.out= length(t))
g2_dvary <- rep(mu2, length.out= length(t))
g3_dvary <- rep(mu3, length.out= length(t))

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g1_dvary + g2_dnull + g3_dnull)
design3 = distributional::dist_normal(g1_dnull + g2_dvary + g3_dnull)
design4 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dvary)
design5 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dvary)

data_bind <- tibble::tibble(
index = t,
g1 = g1,
g2 = g2,
g3 = g3,
design1 = distributional::generate(design1, times = 1) %>% unlist(),
design2 = distributional::generate(design2, times = 1) %>% unlist(),
design3 = distributional::generate(design3, times = 1) %>% unlist(),
design4 = distributional::generate(design4, times = 1) %>% unlist(),
design5 = distributional::generate(design5, times = 1) %>% unlist()
) %>% 
  pivot_longer(-c(1, 2, 3, 4), names_to = "design", values_to = "sim_data")

t = 300
mu1= c(0, 2)
mu2 = c(2, 1, 0)
mu3 = c(0, 1, 2, 1, 0)

data_bind <- generate_design(t, mu1, mu2, mu3)

@@

(p1 + (p2 + p3 + p4)) *
  theme_validation() + plot_layout(widths = c(2, 1))
# 
# plot_cyclic_data( data_bind %>% filter(design=="design2"))
# plot_data( data_bind %>% filter(design=="design3"))
# plot_data( data_bind %>% filter(design=="design4"))
# plot_data( data_bind %>% filter(design=="design5"))
```

@@

```{r gran2and1-clubbed, fig.cap=" For the left scenario $g1$, $g2$ would change across atleast one design but $g3$ change remains same across all design. For tthe right one, only $g3$ changes across different designs."}
#gran2_change  + gran1_change + plot_layout(widths = c(1,1))
ggpubr::ggarrange(gran1_change, gran2_change, labels = c("a", "b"))
```

>>>>

```{r tab-distribution}
```

```{r tab-design}
```

```{r tab-dist-design}
```

```{r generate-design-3change}

@@

@@

```{r generate-design-new}

```{r generate-design-2gran-data}

```{r generate-design-2gran-plot}

```{r generate-design-1gran-data}

```{r generate-design-1gran-plot}

```{r gran2and1-clubbed, fig.cap=" For the left scenario $g1$, $g2$ would change across atleast one design but $g3$ change remains same across all design. For tthe right one, only $g3$ changes across different designs."}
#gran2_change  + gran1_change + plot_layout(widths = c(1,1))
#ggpubr::ggarrange(gran1_change, gran2_change, labels = c("a", "b"))
```
